---
title: "New Presentation"
author: "Robert Miller"
date: "4/28/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## My new slide
```{r comment = "", echo=TRUE }
head(mtcars)

```

## Mtcars Plot
```{r, echo=TRUE, fig.align='center', fig.cap='Fig. 1: Mtcars'}
plot(mtcars$wt, mtcars$mpg, xlab = "Weight", ylab= "MPG")
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```


## Your First Map
```{r, echo=FALSE}
library(leaflet)
my_map<-leaflet() %>%
    addTiles()
my_map = leaflet()
my_map= addTiles(my_map)
my_map

```
